A statistical analysis of a counterstrike game: Boston 2018

### 2019-12-12 inst/counterstrike.Rmd
use equalp()

```{r, random2}
equalstrengths <- rep(0.1, 9)
datapoint <- loglik(indep(maxp(H)),H) - loglik(equalstrengths,H)

n <- 100  # takes about 5 minutes for n=1000 trials
distrib <- rep(0,n)
for(i in seq_len(n)){
  Hrand <- hyper2(pnames=c(team1,team2))
  for(jj in 1:6){
    pp <- rdeath(team1,team2)
    Hrand <- Hrand + counterstrike_maker(team1,team2, pp)
	}
  distrib[i] <- loglik(indep(maxp(Hrand)),Hrand) - loglik(equalstrengths,Hrand)
}

>>>>

```{r, random2}

datapoint <- loglik(indep(maxp(H)),H) - loglik(indep(equalp(H)),H)

n <- 100  # takes about 5 minutes for n=1000 trials
distrib <- rep(0,n)
for(i in seq_len(n)){
  Hrand <- hyper2(pnames=c(team1,team2))
  for(jj in 1:6){
    pp <- rdeath(team1,team2)
    Hrand <- Hrand + counterstrike_maker(team1,team2, pp)
	}
  distrib[i] <- loglik(indep(maxp(Hrand)),Hrand) - loglik(indep(equalp(H)),Hrand)
}
